### 2020-06-12 chapters/sota.tex
More pseudocode

\subsection{Two-Stacks}
The Two-Stacks SWAG algorithm works for \textit{associative} aggregations in scenarios where the sliding window has First-In First-Out (FIFO) semantics --- \textit{i.e.} elements are evicted in the same order they were inserted. Two-Stacks \cite{Tangwongsan-DABA} implements the FIFO queue using two stacks, namely the front stack F and the back stack B. Each element in each of the stacks is a pair \textit{<val, agg>} where \textit{val} is the item's value and \textit{agg} is the aggregation value of everything below it on the stack. The pseudocode for Two-Stacks can be seen in Figure \ref{fig:pseudo-2-stacks}, with $\oplus$ as the \textit{combine} function and $\overline{\theta}$ as the identity value of the \textit{combine} function, such that $\overline{\theta} \oplus x$ = $x \oplus \overline{\theta}$ = x. For example, if $\oplus$ is the arithmetic sum then $\overline{\theta}$ is 0. If $\oplus$ is the arithmetic multiplication then $\overline{\theta}$ is 1.

@@

\begin{figure}[!htb]
    \begin{center}
      \includegraphics[scale=0.45]{figures/2-stacks.png}
      \caption{Two-Stacks algorithm}
      \label{fig:pseudo-2-stacks}
    \end{center}
\end{figure}

@@

\textbf{TODO: Add table with SWAG algorithms, time and space complexity and applicable restrictions on the aggregation}

>>>>

\subsection{Two-Stacks}
The Two-Stacks SWAG algorithm works for \textit{associative} aggregations in scenarios where the sliding window has First-In First-Out (FIFO) semantics --- \textit{i.e.} elements are evicted in the same order they were inserted. Two-Stacks \cite{Tangwongsan-DABA} implements the FIFO queue using two stacks, namely the front stack F and the back stack B. Each element in each of the stacks is a pair \textit{<val, agg>} where \textit{val} is the item's value and \textit{agg} is the aggregation value of everything below it on the stack. The pseudocode for Two-Stacks can be seen in Algorithm \ref{pseudo:2-stacks}, with $\oplus$ as the \textit{combine} function and $\overline{\theta}$ as the identity value of the \textit{combine} function, such that $\overline{\theta} \oplus x$ = $x \oplus \overline{\theta}$ = x. For example, if $\oplus$ is the arithmetic sum then $\overline{\theta}$ is 0. If $\oplus$ is the arithmetic multiplication then $\overline{\theta}$ is 1.

@@

\begin{algorithm}
    \caption{Two-Stacks insert, evict and query methods}
    \label{pseudo:2-stacks}
    \begin{algorithmic}[1]
        \Function{getStackAggregationValue}{stack}
         \If{stack.isEmpty()} 
            \State \Return{$\overline{\theta}$} 
        \Else 
            \State \Return{stack.top().agg} 
        \EndIf
        \EndFunction

        \Function{query}{F, B}
            \State \Return{getStackAggregationValue(F) $\oplus$ getStackAggregationValue(B)}
        \EndFunction

        \Function{insert}{B, v}
            \State{B.push(v, getStackAggregationValue(B) $\oplus$ v}
        \EndFunction

        \Function{evict}{F, B}

            \If{F.isEmpty()} \Comment{// Flip B onto F and update aggregation value}
                \While {\textbf{not} B.isEmpty()}
                    \State{F.push(B.top().val, B.top().val $\oplus$ getStackAggregationValue(F))}
                    \State{B.pop()}
                \EndWhile
            \EndIf
            \State{F.pop()}
        \EndFunction
    \end{algorithmic}
\end{algorithm}

@@

\textcolor{red}{TODO: Add table with SWAG algorithms, time and space complexity and applicable restrictions on the aggregation}
